### 2015-05-13 Draft/approach.tex
Updated Approach
Removed Algorithms to save space

A key way of identifying reference to a method in the API by \tool\ is the employment of a semantic graph of an API.
We propose to initially infer such graphs from API documents.
Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.

We first consider the name of the class for the API document in question.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

\begin{figure}
	\centering
		\includegraphics[scale=0.4]{KnowledgeGraph.eps}
	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
	\label{fig:knowledge}
\end{figure}

We then systematically inspect the member methods to identify actions applicable to the objects represented by the class. From the name of a public method (describing a possible action on the object), we extract verb phrases. The verb phrases are used as the associated actions applicable on the object. In case of REST API we first identified the resources and then listed REST actions on those resources as applicable actions. Figure~\ref{fig:knowledge} shows the graph for \CodeIn{Object} resource in REST API. The phrases in rounded rectangle are the REST actions applicable on \CodeIn{Object} resource in \amazonAPI.

@@

Some temporal constraints are enforced by the type system in typed Languages.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
in the type system. Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.

The algorithm accepts the list of methods as an input produces a graph with
the nodes representing methods in an API and the directed edges representing temporal constraints.
First, an index is created based on the return types of the method (Line 2).
Second, all methods in an API are added to an unconnected graph (Line 3-4).
Then, for every public method in the input list, the algorithm checks the types
of the input parameters and constructs and directed edge from all the methods whose return value
have the same type to the method in question (Line 14- 20).
The algorithm does not take into consideration the basic parameter types such as \CodeIn{integer}, \CodeIn{string} (Line 15).
Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
The resultant graph is then returned by the algorithm.

The temporal constraints based on the type information can be extracted by querying the graph. 
The incoming edges to a node denoting a method represents the set of pre-requisite methods.
The temporal constraint being, at least one of the pre-requisite methods must be invoked before invoking the method in question.

\begin{algorithm}[t!]
\begin{algorithmic}[1]
\begin{scriptsize}
\REQUIRE List $methodList$ 
\ENSURE Graph $seq\_Graph$
\STATE $Graph\ seq\_Graph\ =\ \phi$
\STATE $Map\ idx\ = createIdx(methodList)$

\FORALL{$Method\ mtd\ in\ methodList$} 
	\STATE $seq\_Graph.addVertex(mtd)$
\ENDFOR

\FORALL{$Method\ mtd\ in\ methodList$} 
	\IF{$mtd.isPublic()$}
		\IF{$!mtd.isStatic()$}
			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
			\FORALL{$Method\ mtd'\ in\ preList$}
				\STATE $seq\_Graph.addEdge(mtd',mtd)$
			\ENDFOR
		\ENDIF
		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
			\IF{$!isBasicType(param.Type)$}
				\STATE $List\ preList\ =\ idx.query(paramType)$
				\FORALL{$Method\ mtd'\ in\ preList$}
					\STATE $seq\_Graph.addEdge(mtd',mtd)$
				\ENDFOR				
			\ENDIF
		\ENDFOR
	\ENDIF
\ENDFOR
\RETURN $seq\_Graph$
\end{scriptsize}
\end{algorithmic}
\caption{Type\_Sequence\_Builder}
\label{alg:TypeAnalysis}
\end{algorithm}

>>>>

A key way of identifying reference to a method in the API by \tool\ is the employment of a semantic graph of an API.
We propose to initially infer such graphs from API documents.
Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in Whyper ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.

We first consider the name of the class for the API document in question.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by splitting the camel-case notation in the class name.
This list is further augmented with the name of the parent classes and implemented interfaces if any. We then systematically inspect the member methods to identify actions applicable to the objects represented by the class. From the name of a public method (describing a possible action on the object), we extract verb phrases. The verb phrases are used as the associated actions applicable on the object. In case of REST API we first identified the resources and then listed REST actions on those resources as applicable actions. Figure~\ref{fig:knowledge} shows the graph for \CodeIn{Object} resource in REST API. The phrases in rounded rectangle are the REST actions applicable on \CodeIn{Object} resource in \amazonAPI.

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{KnowledgeGraph.eps}
	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
	\label{fig:knowledge}
\end{figure}

@@

Some temporal constraints are enforced by the type system in typed Languages.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
in the type system. %Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.

%The algorithm accepts the list of methods as an input produces a graph with
%the nodes representing methods in an API and the directed edges representing temporal constraints.
First, an index list ($L_{mtd}$) of the public methods in an API is created based on the return types of the method.
Next, all public methods in the API are added as nodes ($m_1,m_2...m_k$) in an unconnected graph ($G$).
Next, for every method ($m$) in $L_{mtd}$, we identify the types
of the input parameters ($t_1,t_2...t_k$).
We then add a directed edge from all the methods in ($G$), where the return type of the method matches any of the types in ($t_1,t_2...t_k$). 
Additionally, an edge is created from the object creation methods (constructors) of a class to the non-static members methods of a class, because a member methods are invoked after objects creation. 
The temporal constraints based on the type information is extracted by querying $G$. 
The incoming edges to a node denoting a method represents the set of pre-requisite methods.
The temporal constraint being, at least one of the pre-requisite methods must be invoked before invoking the method in question.

%\begin{algorithm}[t!]
%\begin{algorithmic}[1]
%\begin{scriptsize}
%\REQUIRE List $methodList$ 
%\ENSURE Graph $seq\_Graph$
%\STATE $Graph\ seq\_Graph\ =\ \phi$
%\STATE $Map\ idx\ = createIdx(methodList)$
%
%\FORALL{$Method\ mtd\ in\ methodList$} 
%	\STATE $seq\_Graph.addVertex(mtd)$
%\ENDFOR
%
%\FORALL{$Method\ mtd\ in\ methodList$} 
%	\IF{$mtd.isPublic()$}
%		\IF{$!mtd.isStatic()$}
%			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
%			\FORALL{$Method\ mtd'\ in\ preList$}
%				\STATE $seq\_Graph.addEdge(mtd',mtd)$
%			\ENDFOR
%		\ENDIF
%		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
%			\IF{$!isBasicType(param.Type)$}
%				\STATE $List\ preList\ =\ idx.query(paramType)$
%				\FORALL{$Method\ mtd'\ in\ preList$}
%					\STATE $seq\_Graph.addEdge(mtd',mtd)$
%				\ENDFOR				
%			\ENDIF
%		\ENDFOR
%	\ENDIF
%\ENDFOR
%\RETURN $seq\_Graph$
%\end{scriptsize}
%\end{algorithmic}
%\caption{Type\_Sequence\_Builder}
%\label{alg:TypeAnalysis}
%\end{algorithm}

### 2015-05-13 Draft/evaluation.tex
Updated Approach
Removed Algorithms to save space

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%. There is also a slight increase in the recall (average 1\% gain).

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI. On one hand, Java is a widely used programming language and \CodeIn{java.io} is one of the main packages. In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Finally, \paypalAPI\ provides a REST support for online financial transactions. The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.

>>>>

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precision} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%. There is also a slight increase in the recall (average 1\% gain).

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of three different APIs: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI. On one hand, Java is a widely used programming language and \CodeIn{java.io} is one of the main packages. In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Finally, \paypalAPI\ provides a REST support for online financial transactions. The difference in the functionality provided by the three APIs also address the issue of over-fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects APIs.
